Combining neural networks and geostatistics for landslide hazard assessment of San Salvador Metropolitan Area, El Salvador \newline \newline Combinando redes neuronales y geoestad\'{i}stica para evaluaci\'{o}n de deslizamientos de tierra del \'{a}rea Metropolitana de San Salvador, El Salvador

### 2015-09-11 paper.tex

\documentclass[11pt,twoside]{rmta2010esp}% For English, use rmta2010eng.cls instead of rmta2010esp.cls
%\pagestyle{myheadings} 
\usepackage[english, spanish]{babel}
\usepackage{fancyhdr}
\usepackage[utf8]{inputenc} % En caso de usar tildes, y otros caracteres especiales

\pagestyle{fancy}
\fancyhead{}
\fancyhead[RE]{\thepage \hfill {\sc r. r\'{i}os -- a. rib\'{o} -- r. mej\'{i}a -- g. molina }}
\fancyhead[LO]{{\sc Combining neural networks and geostatistics for landslide hazard assessment of San Salvador Metropolitan Area, El Salvador } \hfill \thepage}
\fancyfoot{}
\fancyfoot[RE]{{\scriptsize{\it Rev.Mate.Teor.Aplic.} (ISSN 1409-2433) {Vol. 19}(1): 1--10, January 2012}}
\fancyfoot[LO]{{\scriptsize{\it Rev.Mate.Teor.Aplic.} (ISSN 1409-2433) {Vol. 19}(1): 1--10, January 2012}}
\paginas{1}{10} % Numeros de pgina, la versión final la pone el editor; Page numbers, the Editor puts the final numbers
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphics}
\usepackage{graphicx} % En caso de usar figuras, con formato .esp; In case of using figures, with format .eps
\usepackage{float} 
\usepackage{url}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{enumerate}
\usepackage{authblk}
\usepackage{hyperref}
\usepackage{textcomp}

@@

@@

 \begin{center}
  \begin{figure}
   \centering
   \includegraphics[scale=0.70]{MASS_mapa_1}
   \caption{\small{Location of El Salvador in Central America, map of El Salvador with location of the Metropolitan Area of San Salvador (MASS) and its topography.}}
   \label{fig:mass01}
  \end{figure}
 \end{center}

@@

The results obtained through geostatistical methodology met the assumptions for kriging method application. Final map of landslide probability of occurrence (see Fig. \ref{fig:mass02} ) generated by kriging method was the result of multidisciplinary work which implied an intense geological analysis (i.e. MARN inventory of 4792 landslides), together with the use of sophisticated statistical techniques. This landslide hazard map is a user-friendly tool to evaluate landslide risk in MASS and can be useful for many purposes such as territorial planning, prevention and landslide mitigation and so on. 
\begin{center}
  \begin{figure}
   \centering
   \includegraphics[scale=0.73]{MASS_mapa_2}
   \caption{\small{Landslide hazard map MASS where the landslide probability of occurrence is shown.}}
   \label{fig:mass02}
  \end{figure}
 \end{center}
High probability of landslide occurrence in Picacho slope implies very high risk due to the proximity of urban areas and due to the large volume of mobilized materials. Major et al.\cite{major2004} identified in San Salvador volcano lahars as voluminous as 2 million of $m^{3}$ that can affect large zones of urban areas. Southern areas of MASS also have a high risk because landslides, similar to Las Colinas landslide which involved a total volume of around 200,000 $m^{3}$ \cite{evans}, can occur in northern slope of Balsamo range and San Jacinto Hill, affecting very crowded urban areas.

>>>>

\documentclass[11pt,twoside]{rmta2010eng}% For English, use rmta2010eng.cls instead of rmta2010esp.cls
%\pagestyle{myheadings} 
\usepackage[english, spanish]{babel}
\usepackage{fancyhdr}
\usepackage[utf8]{inputenc} % En caso de usar tildes, y otros caracteres especiales

\pagestyle{fancy}
\fancyhead{}
\fancyhead[RE]{\thepage \hfill {\sc r. r\'{i}os -- a. rib\'{o} -- r. mej\'{i}a -- g. molina }}
\fancyhead[LO]{{\sc Combining neural networks and geostatistics for landslide hazard assessment of San Salvador Metropolitan Area, El Salvador } \hfill \thepage}
\fancyfoot{}
\fancyfoot[RE]{{\scriptsize{\it Rev.Mate.Teor.Aplic.} (ISSN 1409-2433) {Vol. 19}(1): 1--10, January 2012}}
\fancyfoot[LO]{{\scriptsize{\it Rev.Mate.Teor.Aplic.} (ISSN 1409-2433) {Vol. 19}(1): 1--10, January 2012}}
\paginas{1}{10} % Numeros de pagina, la version final la pone el editor; Page numbers, the Editor puts the final numbers
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphics}
\usepackage{graphicx} % En caso de usar figuras, con formato .esp; In case of using figures, with format .eps
\usepackage{float} 
\usepackage{url}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{enumerate}
\usepackage{authblk}
\usepackage{hyperref}
\usepackage{textcomp}
\usepackage[T1]{fontenc} % Setting Times New Roman font 
\usepackage{mathptmx}    % Setting Times New Roman font

\usepackage{geometry}
 \geometry{
 a4paper,
 textwidth=15cm, 
 textheight=21cm
 }

@@

\date{}

@@

 \begin{center}
  \begin{figure}
   \centering
   \includegraphics[scale=0.70]{MASS_map_1.eps}
   \caption{\small{Location of El Salvador in Central America, map of El Salvador with location of the Metropolitan Area of San Salvador (MASS) and its topography.}}
   \label{fig:mass01}
  \end{figure}
 \end{center}

@@

The results obtained through geostatistical methodology met the assumptions for kriging method application. Final map of landslide probability of occurrence (see Fig. \ref{fig:mass02} ) generated by kriging method was the result of multidisciplinary work which implied an intense geological analysis (i.e. MARN inventory of 4792 landslides), together with the use of sophisticated statistical techniques. This landslide hazard map is a user-friendly tool to evaluate landslide risk in MASS and can be useful for many purposes such as territorial planning, prevention and landslide mitigation and so on. 
\begin{center}
  \begin{figure}
   \centering
   \includegraphics[scale=0.73]{MASS_map_2.eps}
   \caption{\small{Landslide hazard map MASS where the landslide probability of occurrence is shown.}}
   \label{fig:mass02}
  \end{figure}
 \end{center}
High probability of landslide occurrence in Picacho slope implies very high risk due to the proximity of urban areas and due to the large volume of mobilized materials. Major et al.\cite{major2004} identified in San Salvador volcano lahars as voluminous as 2 million of $m^{3}$ that can affect large zones of urban areas. Southern areas of MASS also have a high risk because landslides, similar to Las Colinas landslide which involved a total volume of around 200,000 $m^{3}$ \cite{evans}, can occur in northern slope of Balsamo range and San Jacinto Hill, affecting very crowded urban areas.
